Automated Dynamic Slice Backsolving

### 2014-03-23 docs/paper/fsuthesis/thesis-template/paper.tex
no big changes, getting some chocolate before i finish impl, parallel sections and proofread background

SAGE uses symbolic execution, and prunes paths taken with a propietary "generational search" algorithm. This algorithm prioritizes generating new test cases. It takes a set of all constraints and tries negating each constraint independently to generate a new test case. SAGE then symbolically re-executes the constraint set using TruScan [TODO CITE] [Q]. Similarly, s2e uses QEMU for instruction set emulation, and then appears to be a strong trend in white-box fuzzing. TODO ADV/DIS?

@@

%TODO Peach Fuzzer does both, overview with pictures?

@@

%TODO add code examples
%http://en.wikipedia.org/wiki/User_Datagram_Protocol#IPv4_Pseudo_Header
%IDEA write c program to checksum UDP packets and say whether they pass or not, have fuzzer "correct" packets to pass arbitrary, user decided checksum.
%update: probably will not work without noticeable modification, but could maybe notice the situation and reverse engineer the algorithm, then print it out or start making a lookup table?

@@

While finding bugs of any sort enhances software by providing developers the opportunity to fix problems with their programs, finding bugs that lead to exploitable conditions are of special interest. A bug is exploitable if it allows adveraries to undermine confidentiality, integrity, or availability [CITE] via avenues such as information disclosure, denial of service, or remote execution of code. Because these bugs stand alone as a separate, particularly worrying class, efforts have been made to automate the process of proving whether an identified bug is also a vulnerability which can be exploited.

@@

TODO Mayhem techniques

@@

TODO similar to Automatic patch-based exploit generation is possible: Techniques and
implications, but mine doesn't require a patch?

%\section{TODO Argos: 0-Day Emulator}

@@

% TODO check if mention Pin compiles from x86 to x86 adding pintool

@@

\subsection{TODO Conversion to an Intermediate Representation}

Used in javascript fuzzer [AD]
Used in [C].
Mitigates dealing with side effects, done by PANDA.
%http://www.cc.gatech.edu/~brendan/tzb_author.pdf
%http://iris.lib.neu.edu/cgi/viewcontent.cgi?article=1097&context=elec_comp_theses

@@

we ignore ....loops, more TODO

@@

TODO Stubble architecture, describe
why intel pin and not dynamo rio, valgrind, etc.

@@

TODO attacks which transform input first to show ability to backsolve

@@

\addplot[
    color=red,
    mark=square,
    ]
    coordinates {
    		(1,19)
    		(5,30)
    		(10,31)
    		(15,45)
    		(20, 53)
    		(25, 101) 
    		(30, 112)
    		(35, 129) 
    		(40, 140)
    		(45, 157) 
    		(50, 172) 
    };

% TODO find a way to label these

\end{axis}
\end{tikzpicture}
\end{figure}

%\chapter{Old Contributions}

%\section{Assumptions and Scoping}

%TODO in above make sure can catch stderr segfaults, segfaults go to shell's stderr, also a signal, test this

%Current selective symbolic execution engines still appear to introduce significant overhead, between 6 and 78X overhead more than QEMU for S2E. Just QEMU is between 4 and 10 times slower on some benchmarks, closer to 15 on others [J, K, L]. In contrast, basic block counting using Intel Pin, the framework we are leveraging, introduced between 2 and 4X overhead [M]. However, the pintool needed for our proposed technique introduces greater levels of overhead, since we will be working at the instruction level instead of the basic block level, requiring more insertions for any given binary.

@@

% TODO We then plan to test against S2E and Peach Fuzzer [Z].

>>>>

SAGE uses symbolic execution, and prunes paths taken with a propietary "generational search" algorithm. This algorithm prioritizes generating new test cases. It takes a set of all constraints and tries negating each constraint independently to generate a new test case. SAGE then symbolically re-executes the constraint set using a trace analysis engine [Q]. Similarly, s2e uses QEMU for instruction set emulation, and then appears to be a strong trend in white-box fuzzing.

@@

@@

%TODO add code examples?

@@

While finding bugs of any sort enhances software by providing developers the opportunity to fix problems with their programs, finding bugs that lead to exploitable conditions are of special interest. A bug is exploitable if it allows adveraries to undermine confidentiality, integrity, or availability via avenues such as information disclosure, denial of service, or remote execution of code. Because these bugs stand alone as a separate, particularly worrying class, efforts have been made to automate the process of proving whether an identified bug is also a vulnerability which can be exploited.

@@

@@

%TODO similar to Automatic patch-based exploit generation is possible: Techniques and
implications, but mine doesn't require a patch?

@@

@@

@@

@@

TODO why intel pin and not dynamo rio, valgrind, etc.

@@

@@

\addplot[
    color=red,
    mark=square,
    ]
    coordinates {
    		(1,19)
    		(5,30)
    		(10,31)
    		(15,45)
    		(20, 53)
    		(25, 101) 
    		(30, 112)
    		(35, 129) 
    		(40, 140)
    		(45, 157) 
    		(50, 172) 
    };     
\end{axis}
\end{tikzpicture}
\end{figure}

% TODO add these back in?
%Current selective symbolic execution engines still appear to introduce significant overhead, between 6 and 78X overhead more than QEMU for S2E. Just QEMU is between 4 and 10 times slower on some benchmarks, closer to 15 on others [J, K, L]. In contrast, basic block counting using Intel Pin, the framework we are leveraging, introduced between 2 and 4X overhead [M]. However, the pintool needed for our proposed technique introduces greater levels of overhead, since we will be working at the instruction level instead of the basic block level, requiring more insertions for any given binary.

@@
